\large{Vipassana for Hackers} \\ \Huge{Paper Four: Mastering Spacetime} \\ \large\textit{Version 0.1}

### 2019-12-25 paper-four/paper-four.tex
one last note for p4
first commit on the proposal... here we go.
p4: abstract and target audience

\begin{abstract}
 \todo{Write the abstract.}
\end{abstract}

@@

The target audience for this paper remains ``hackers'' for the broadest possible
definition of that word. \todo{ref: from cherry?}

\begin{itemize}
  \item Old students (Goenka; forward ref other methods of learning)
  \item People looking to deepen practice
  \item Meditators who haven't chosen a technique yet
\end{itemize}

@@

Anapana eliminates space.

@@

>>>>

\begin{abstract}
 \todo{After someone has completed their first 10-day Vipassana course there often
   remain a number of open questions regarding the practice. How, exactly, is the
   meditation removing mental negativities? Is this really the be-all-end-all of
   meditation techniques? Is the teaching methodology really systematic and global?
   This paper attempts to answer these questions and others.}
\end{abstract}

@@

The target audience for this paper remains ``hackers'' for the broadest possible
definition of that word. \todo{add ref: Hackers book} If you are a curious and
analytical person, you qualify. The new restriction placed on this paper is that you
must have \textit{completed} at least one 10-day Vipassana course (as taught by
S.N. Goenka). To ``complete'' the course means that you left the course centre on the
eleventh day and no sooner. Although Sayagyi U Ba Khin authorized many other teachers
in addition to S.N. Goenka, the portions of this paper which deal with the systematic
and global approach to the teaching require taking a course from S.N. Goenka or one
of his authorized Assistant Teachers. Sayagyi U Ba Khin's other students did not
construct comparably systematic teaching methods.

This paper will discuss alternative methods of Vipassana instruction to S.N. Goenka's
system but even those discussions will be within the context of S.N. Goenka's
instruction as the global standard.

Readers may have chosen to dedicate their lives to the technique of Vipassana or they
may still be searching. Portions of this paper will be dedicated to analyzing reasons
to dedicate oneself to a single technique --- as well as merits and drawbacks of
choosing Vipassana as that technique.

The paper is best suited to Vipassana meditators who are looking to deepen and expand
their practice. It is important to remember, however, that this paper is authored by
non-teaching meditators and is no replacement for expert advice from a trained and
authorized Assistant Teacher.

With these restrictions in mind, anyone is of course welcome to read the
paper. However, much of what is being said will seem unnecessarily recondite to
someone without the requisite practical meditation experience.

@@

Anapana eliminates space. Continuity is the source of constantly-narrowing attention on space.

@@

- structure: the requirement that meditation be taught for free (expand)
